Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)

### 2022-12-02 R/model_fcs_check.Rmd
Update model_fcs_check.Rmd

---
title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)"
author: "<b>Markus Bauer*</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: jpeg
    fig_width: 7
    fig_height: 5
---

@@

## Model building

### Models

Model caluclations

@@

### Model check

#### DHARMa

@@

#### Preparation

@@

#### Sampling efficency and effectiveness

Rhat

@@

Effective sampling size (ESS)

@@

#### MCMC diagnostics

@@

#### Posterior predictive check

##### Kernel density

@@

##### Histograms of statistics skew

@@

##### LOO (Leave one out)

@@

#### Autocorrelation check

>>>>

---
title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)"
author: "<b>Markus Bauer*</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: png
    fig_width: 7
    fig_height: 5
    df_print: tibble
---

@@

## Models

@@

## Model check

### DHARMa

@@

### Preparation

@@

### Sampling efficency and effectiveness

#### Rhat

@@

#### Effective sampling size (ESS)

@@

### MCMC diagnostics

@@

### Posterior predictive check

#### Kernel density

@@

#### Histograms of statistics skew

@@

#### LOO (Leave one out)

@@

### Autocorrelation check
